---
title: "Regressions"
author: "UNDP Team"
date: "2/25/2020"
output: pdf_document
---

```{r libraries, message=FALSE, warning=FALSE, echo=FALSE}
library(readr)
library(plm)
library(dplyr)
library(ggplot2)
library(dbplyr)
library(plm)
library(tidyverse)


```

#Regresions for Events

##VE Events -> VSC
##Not significant

```{r first_regs, message=FALSE, warning=FALSE, echo=FALSE}
setwd("~/")
merged_data <- read_csv("merged_data.csv")
d1_panel <- pdata.frame(merged_data, index=c("ROUND"))
model <- plm(Events ~ VSC, data=d1_panel, model="within")
summary(model)
d_panel <- pdata.frame(merged_data, index=c("ROUND", "COUNTRY"))


```

##VE Events -> HSC
##Not significant

```{r first_regs1, message=FALSE, warning=FALSE, echo=FALSE}

d2_panel <- pdata.frame(merged_data, index=c("ROUND", "COUNTRY"))
model <- plm(Events ~ HSC, data=d2_panel, model="within")
summary(model)

```


##VE Events -> VSC + HSC
##Not significant


```{r first_regs222, message=FALSE, warning=FALSE, echo=FALSE}

d3_panel <- pdata.frame(merged_data, index=c("ROUND", "COUNTRY"))
model <- plm(Events ~ VSC + HSC, data=d3_panel, model="within")
summary(model)

```

##VE Events -> VSC + HSC + VSC*HSC
##Not significant


```{r first_regs2, message=FALSE, warning=FALSE, echo=FALSE}

d33_panel <- pdata.frame(merged_data, index=c("ROUND", "COUNTRY"))
model <- plm(Events ~ VSC + HSC + VSC*HSC, data=d3_panel, model="within")
summary(model)

```




##VE Events -> VSC (Civic Activism, Democracy, Political Participation, Unequal Treatment by government, Societal Participation)
##Negative, statistically significant for Democracy, and almost Societal participation


```{r second_regs, message=FALSE, warning=FALSE, echo=FALSE}
d_panel5 <- pdata.frame(merged_data, index=c("ROUND", "COUNTRY"))
model <- plm(Events ~ VSC_CA + VSC_DE + VSC_PP + VSC_UG + VSC_SP + HSC_CI + HSC_CS + HSC_IM, data=d_panel, model="within")
summary(model)

```


##VE Events -> HSC (Community Inclusion, Participation in Associations, Inclusion of minorities)
##Only IM Significant

```{r second_regs1, message=FALSE, warning=FALSE, echo=FALSE}

d_panel4 <- pdata.frame(merged_data, index=c("ROUND", "COUNTRY"))
model <- plm(Events ~ HSC_CI + HSC_CS + HSC_IM, data=d_panel, model="within")
summary(model)

```


##Based on the results from previous regressions

##VE Events -> VSC (Democracy, Social Participation)
##Negative, statistically significant for DE


```{r third_regs, message=FALSE, warning=FALSE, echo=FALSE}
d_panel6 <- pdata.frame(merged_data, index=c("ROUND", "COUNTRY"))
model <- plm(Events ~ VSC_DE + VSC_SP, data=d_panel, model="within")
summary(model)

```


##VE Events -> HSC (Inclusion Minorities)
##Negative, statistically significant


```{r third_regs1, message=FALSE, warning=FALSE, echo=FALSE}

d7_panel <- pdata.frame(merged_data, index=c("ROUND"))
model4 <- plm(Events ~ HSC_IM, data=d7_panel, model="within")
summary(model4)
```


##VE Events -> VSC (Democracy), HSC (Inclusion of Minorities)
##NOT statistically significant, almost


```{r fourth_regs1, message=FALSE, warning=FALSE, echo=FALSE}
d_panel8 <- pdata.frame(merged_data, index=c("ROUND", "COUNTRY"))
model <- plm(Events ~ VSC_DE + HSC_IM, data=d_panel, model="within")
summary(model)
```


##VE Events -> VSC (Democracy), HSC (Inclusion of Minorities) with Interaction term
##Negative, statistically significant for all


```{r fourth_regs2, message=FALSE, warning=FALSE, echo=FALSE}
d_panel8 <- pdata.frame(merged_data, index=c("ROUND", "COUNTRY"))
model <- plm(Events ~ VSC_DE + HSC_IM + VSC_DE * HSC_IM, data=d_panel, model="within")
summary(model)
```

#Regressions for Attitudes

##Justification of political violence -> VSC
##Positive, almost significant


```{r fourth_regs3, message=FALSE, warning=FALSE, echo=FALSE}

d_panel <- pdata.frame(merged_data, index=c("COUNTRY", "ROUND"))
model <- plm(VE3 ~ VSC, data=d_panel, model="within")
summary(model)
```

##Justification of political violence -> HSC
##Not significant

```{r fourth_regs4, message=FALSE, warning=FALSE, echo=FALSE}
d_panel <- pdata.frame(merged_data, index=c("COUNTRY", "ROUND"))
model <- plm(VE3 ~ HSC, data=d_panel, model="within")
summary(model)
```


##Justification of political violence -> VSC_DE (democracy) + VSC_UG (unequal treatment)
##Democracy Positive, significant

```{r fourth_regs41, message=FALSE, warning=FALSE, echo=FALSE}
d_panel <- pdata.frame(merged_data, index=c("ROUND", "COUNTRY"))
model <- plm(VE3 ~ VSC_DE + VSC_UG, data=d_panel, model="within")
summary(model)
```


##Justification of political violence -> VSC_DE
##Positive, not significant

```{r fourth_regs42, message=FALSE, warning=FALSE, echo=FALSE}
d_panel <- pdata.frame(merged_data, index=c("COUNTRY", "ROUND"))
model <- plm(VE3 ~ VSC_DE, data=d_panel, model="within")
summary(model)
```





##Violence is justified if it is for a just cause


##Violence is justified if it is for a just cause -> VSC
##Negative, almost significant

```{r fourth_regs5, message=FALSE, warning=FALSE, echo=FALSE}
d_panel <- pdata.frame(merged_data, index=c("COUNTRY", "ROUND"))
model <- plm(VE4 ~ VSC, data=d_panel, model="within")
summary(model)
```


##Violence is justified if it is for a just cause -> HSC
##Not significant

```{r fourth_regs6, message=FALSE, warning=FALSE, echo=FALSE}
d_panel <- pdata.frame(merged_data, index=c("COUNTRY", "ROUND"))
model <- plm(VE4 ~ HSC, data=d_panel, model="within")
summary(model)
```


##Violence is justified if it is for a just cause -> VSC + HSC
##Not significant


```{r fourth_reg72, message=FALSE, warning=FALSE, echo=FALSE}
d_panel <- pdata.frame(merged_data, index=c("COUNTRY", "ROUND"))
model <- plm(VE4 ~ HSC+VSC, data=d_panel, model="within")
summary(model)
```

##Violence is justified if it is for a just cause -> Political participation, Unequal treatment, Civic Activism and Democracy
##not significant


```{r fourth_reg7214, message=FALSE, warning=FALSE, echo=FALSE}
d_panel <- pdata.frame(merged_data, index=c("ROUND", "COUNTRY"))
model <- plm(VE4 ~ VSC_CA + VSC_DE + VSC_PP + VSC_UG, data=d_panel, model="within")
summary(model)
```


##Violence is justified if it is for a just cause -> Political participation, Civic Activism and Democracy
##almost all significant


```{r fourth_reg7213, message=FALSE, warning=FALSE, echo=FALSE}
d_panel <- pdata.frame(merged_data, index=c("ROUND", "COUNTRY"))
model <- plm(VE4 ~ VSC_CA + VSC_DE + VSC_PP, data=d_panel, model="within")
summary(model)
```

##Violence is justified if it is for a just cause -> Political participation and Civic Activism
##significant


```{r fourth_reg7212, message=FALSE, warning=FALSE, echo=FALSE}
d_panel <- pdata.frame(merged_data, index=c("ROUND", "COUNTRY"))
model <- plm(VE4 ~ VSC_CA + VSC_PP, data=d_panel, model="within")
summary(model)
```

##Violence is justified if it is for a just cause -> Community Inclusion, Clubs and Associations
##Not significant


```{r fourth_reg7211, message=FALSE, warning=FALSE, echo=FALSE}
d_panel <- pdata.frame(merged_data, index=c("ROUND", "COUNTRY"))
model <- plm(VE4 ~ HSC_CI + HSC_CS, data=d_panel, model="within")
summary(model)
```










